BSOS

### 2014-06-09 Paper.tex
Added names.
We still need an annotated bibliography.

\part{Operating System Basics}
\paragraph{Theory}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU's operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

@@

\part{Booting Up}
\paragraph{}
BSOS, as a portable and abstracted system, must be capable of bootstrapping on a variety of diverse and divergent architectures. Although hundreds exist, ranging from giants like x86, POWER, and ARM to lesser known embedded architectures like AVR and MIPS, the vast majority fall into one of two families: \textit{CISC} and \textit{RISC}.

@@

\part{Memory Management}

@@

\part{Interfacing With Hardware}
There are 2 main components to input and output for this operating system, keyboard and screen, and motors and sensors.
\paragraph{Keyboard and Screen}
Information is sent from the keyboard to the processor via a standard protocol. Inside any commercial keyboard is a tiny computer chip
called a {\it microcontroller}. When a key is pressed down, the microcontroller receives the signal and starts a short countdown timer. If your finger is still pressing down on the key after more than a millisecond, the microcontroller looks up a numerical value for the key
and saves it in its small memory bank.

>>>>

\part{Operating System Basics-Reyna}
\paragraph{Theory}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU's operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

@@

\part{Booting Up-William}
\paragraph{}
BSOS, as a portable and abstracted system, must be capable of bootstrapping on a variety of diverse and divergent architectures. Although hundreds exist, ranging from giants like x86, POWER, and ARM to lesser known embedded architectures like AVR and MIPS, the vast majority fall into one of two families: \textit{CISC} and \textit{RISC}.

@@

\part{Memory ManagementPawe\l{}}

@@

\part{Interfacing With Hardware-Alex}
There are 2 main components to input and output for this operating system, keyboard and screen, and motors and sensors.
\paragraph{Keyboard and Screen}
Information is sent from the keyboard to the processor via a standard protocol. Inside any commercial keyboard is a tiny computer chip
called a {\it microcontroller}. When a key is pressed down, the microcontroller receives the signal and starts a short countdown timer. If your finger is still pressing down on the key after more than a millisecond, the microcontroller looks up a numerical value for the key
and saves it in its small memory bank.
